\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/architecture.tex
new graph and typos

In \speculake, we cause the CPU to mis-speculate the destination of an indirect
branch in the payload program, causing it to speculatively execute 
instructions that are never truly executed. We term this speculative destination
the \emph{speculative entry point}. \speculake uses indirect jumps to allow
speculatively executing from \emph{any} instruction in the payload process'
address space. Because it can jump to any instruction, the malware analyst has a
difficult task in determining where a payload program's speculative entry point
is.

In fact, the location this entry point is not determined by the payload
program, but rather the corresponding trigger program. This means that with only
the payload program, an analyst does not posses enough information to find the
speculative entry point.

>>>>

In \speculake, we cause the CPU to mis-speculate the destination of an indirect
branch in the payload program, causing it to speculatively execute 
instructions that are never truly executed. We term this speculative destination
the \emph{speculative entry point}. \speculake uses indirect jumps to allow
speculative execution from \emph{any} instruction in the payload process'
address space. Because it can jump to any instruction, the malware analyst has a
difficult task in determining where a payload program's speculative entry point
is.

In fact, the location of this entry point is not determined by the payload
program, but rather the corresponding trigger program. This means that with only
the payload program, an analyst does not posses enough information to find the
speculative entry point.

### 2018-05-09 paper/figures.tex
new graph and typos

    \caption{The number of instructions and success rate of a the 5-state Busy 
    Beaver configuration were measured as a function of how many iterations 
    into the speculative world were performed. We see that the amount of time 
    to reach 20,000 instructions completed is a linear function of how many 
    indirect calls into the speculative world we take. Additionally we see that 
    it only requires using 4 speculative calls to achieve no errors in reaching 
    20,000 instructions.}

>>>>

    \caption{The number of instructions and error rate of a the 5-state Busy
    Beaver configuration were measured as a function of how many iterations into
    the speculative world were performed. We see that the amount of time to
    reach a million instructions completed is a linear function of how many
    indirect calls into the speculative world we take. Additionally we see that
    it only requires using 10 speculative calls per instruction to achieve a
    very low number of errors in reaching a million instructions.}
